{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-08 Paper/main.tex

	As can be seen, differing from the case of Banach spaces, these representations can be limits of series as previously hinted at by using the closed span of the basis. As using an infinite number of basis functions is infeasible in applied contexts, an intuitive way to approximate elements of a Hilbert space is to use a truncated series.
	\begin{equation}
		x \approx \sum_{j = 1}^{K}{\langle x, s_j \rangle}s_j
	\end{equation}

	\subsection{Random Functions in the Hilbert Space of Square-Integrable Functions}
	In functional data analysis, one Hilbert space of particular importance is the space of square-integrable functions on $[0,1]$ denoted $\mathbb{L}^2[0,1]$. To define it, look first at the measure space given by $([0,1], \mathcal{B}, \mu)$ where $\mathcal{B}$ is the Borel $\sigma$-algebra on $[0,1]$ and $\mu$ is the Lebesgue-measure. Then $\mathbb{L}^2[0,1]$ is the collection of all measurable functions $f$ on $[0,1]$ that fulfill the following condition.
	\begin{equation}
		\lvert \lvert f \rvert \rvert_2 = \int_{0}^{1} \lvert f \rvert^2 \mathrm{d}\mu < \infty
	\end{equation}

	This ensures that a random function has a finite second moment so that the variance and covariance functions can be defined. Its inner product is defined.
	\begin{equation}
		\langle f_1, f_2 \rangle = \int_{0}^{1} f_1 f_2 \mathrm{d}\mu.
	\end{equation}

	$\mathbb{L}^2[0,1]$ is the function space that is most often used for theoretical considerations in functional data analysis, but analogous constructions can be made for every closed interval of $\mathbb{R}$. 
	%Therefore, we focus on the interval $[0,1]$ without loss of generality for the purpose of this paper. 
	A random function defined on $\mathbb{L}^2[0,1]$ is a function $X : \Omega \rightarrow \mathbb{L}^2[0,1]$ defined on a common probability space $(\Omega, \mathcal{A}, P)$ where $\Omega$ is a sample space with $\sigma$-algebra $\mathcal{A}$ and a probability space $P$. The realized $X(\omega)(t)$ for every $t \in [0,1]$ is called a sample curve for the process. The collection of such sample curves constitutes a functional data set.

	\subsection{Functional Data Sets}
	Consider the case of a data set containing observations $x_i$ of a random function $X$, measured at discrete points $t_{i,j}$: 
	\begin{equation}
		x_{i}(t_{i,j}) \in \mathbb{R}, \quad i = 1,\: \dots\: ,N, \; j = 1, \: \dots \:, J_i, \; t_{i,j} \in [T_1, T_2]
	\end{equation}

	Each curve $x_i(t)$ exists $\forall t \in [T_1, T_2]$, but is only observed at discrete measurement points. The measurement points can be different for each sample. However, this is not a primary interest of this paper, and, therefore, we consider the case where curves are observed at a shared set of measuring points. In principle, these measurements can be seen as a discretized approximation of a realization of a random function. It causes necessities to represent the functional data with respect to some expansion technique. One technique to make the functional data smooth, truncated basis expansion, is introduced in the following sections.\\
	As in the finite-dimensional setting, the concept of identically distributed and independent data is important for many aspects of functional data analysis, such as, for example, many inferential procedures. One example could be a set of NIR absorption spectra of gasoline samples in which curves are observed at a shared set of wavelengths and each sample stemming from the same production can be seen as a realization of the same random process.

>>>>

	Differing from the case of Banach spaces, these representations can be limits of series. As using an infinite number of basis functions is infeasible in applied contexts, an intuitive way to approximate elements in a Hilbert space is to use a truncated series.
	\begin{equation}
		x \approx \sum_{j = 1}^{K}{\langle x, s_j \rangle}s_j
	\end{equation}

	\subsection{Random Functions in the Hilbert Space of Square-Integrable Functions}
	In functional data analysis, one Hilbert space of particular importance is the space of square-integrable functions on $[0,1]$. Denoted by $\mathbb{L}^2[0,1]$, this space is consists of all $\mu$-measurable functions $f(t)$ on $[0,1]$ that fulfill the following condition in which $\mu$ denotes the Lebesgue-measure.
	\begin{equation}
		\lvert \lvert f \rvert \rvert_2 = \int_{0}^{1} \lvert f \rvert^2 \mathrm{d}\mu < \infty
	\end{equation}

	This ensures that a random function has a finite second moment so that the variance and covariance functions can be defined. The inner product of $\mathbb{L}^2[0,1]$ is defined by Equation \ref{inner_prod}.
	\begin{equation}\label{inner_prod}
		\langle f_1, f_2 \rangle = \int_{0}^{1} f_1 f_2 \mathrm{d}\mu.
	\end{equation}

	$\mathbb{L}^2[0,1]$ is the function space that is most often used for theoretical considerations, but analogous constructions can be made for every closed interval of $\mathbb{R}$. 
	A random function on $\mathbb{L}^2[0,1]$ can then be defined formally as a function $X : \Omega \rightarrow \mathbb{L}^2[0,1]$ defined on a probability space $(\Omega, \mathcal{A}, P)$ where $\Omega$ is a sample space with $\sigma$-algebra $\mathcal{A}$ and a probability space $P$.

	\subsection{Functional Data Sets}
	If we take a random function $X(\omega)$ as defined in the previous section, then realizations $x(t)$ of $X(\omega)(t)$ are called sample curves of the random function. The presence of functional observations in a data set is what defines functional data sets. However, in reality realizations of random functions are not typically observed in their functional form. Instead, each curve is observed at a discrete and typically large set of measurements points. Consider the case of a data set containing observations $x_i(t)$ of a random function $X(\omega)$
	\begin{equation}
		x_{i}(t_{i,j}) \in \mathbb{R}, \quad i = 1,\: \dots\: ,N, \; j = 1, \: \dots \:, J_i, \; t_{i,j} \in [T_1, T_2]
	\end{equation}

	Each curve $x_i(t)$ exists $\forall t \in [T_1, T_2]$, but is only observed at discrete measurement points $t_{i,j}$. These measurement points can be different for each sample curve. However, in this paper, we only consider the case where curves share their measuring points. 
	To work with functional data obtained in this form using the unique capabilities of functional data analysis, it is necessary to restore its functional structure. Therefore, methods such as basis representations, which are introduced in the following parts of the Theory Section, are necessary.\\

	As in the finite-dimensional setting, the concept of identically distributed and independent data is important for many aspects of functional data analysis. One example of i.i.d. curves could be Near-Infrared absorption spectra of gasoline samples where each sample is produced by the same production process and can therefore be interpreted as a realization of and i.i.d. random process itself.
